Playground for PNAS cover graphic

### 2021-11-04 cover/cover.Rmd

```{r trend-plots}
names <- c("Reported COVID cases", 
           "COVID symptoms in medical claims", 
           "Self-reported COVID symptoms in surveys",
           "Searches for COVID symptoms on Google")
colors <- c("#FFFFFF", "#E69F00", "#56B4E9", "#CC79A7")

g <- vector(mode = "list", length = length(x))
delta <- 1/500
alpha <- 0.35
ylim <- c(-0.05, 1.05 + 50 * delta)

for (i in 1:length(x)) {
  g[[i]] <- x[[i]] %>%
    filter(geo_value %in% tolower(state.abb)) %>%
    mutate(geo_num = as.integer(as.factor(geo_value))) %>%
    group_by(geo_value) %>%
    mutate(value = (value - Min(value)) / (Max(value) - Min(value)) + 
             delta * (geo_num - 1)) %>%
    ungroup() %>%
    ggplot(aes(x = time_value, y = value, group = geo_value)) +
    labs(y = names[i]) + coord_cartesian(ylim = ylim) +
    geom_line(alpha = 0.5, color = colors[i]) + theme_void() +
    theme(panel.background = element_rect(fill = "black"),
          axis.title.y = element_text(color = colors[i], angle = 90,
                                      margin = margin(l = 10, r = -15)))
}

pdf(file = "cover-graphic.pdf", width = 15, height = 15)
do.call(gridExtra::marrangeGrob, list(g, nrow = 5, ncol = 1))
graphics.off()
```

>>>>

```{r trend-plots}
names <- c("Reported COVID cases",
           "COVID symptoms\nin medical claims",
           "Self-reported COVID\nsymptoms in surveys",
           "Searches for COVID\nsymptoms on Google")
colors <- c("#FFFFFF", "#E69F00", "#56B4E9", "#CC79A7")

dates <- seq.Date(start, end, by = "1 day")
n_days <- length(dates)

g <- vector(mode = "list", length = length(x))
delta <- 1/500
alpha <- 0.35
xlim <- c(start - 10, end)
ylim <- c(-0.05, 1.05 + 50 * delta)
xp <- xlim[1] - 8
yp <- mean(ylim)

for (i in 1:length(x)) {
  y <- tibble(geo_value = rep(unique(x[[i]]$geo_value), each = n_days),
              time_value = rep(seq.Date(start, end, by = "day"),
                               length(unique(x[[i]]$geo_value))))
  x[[i]] <- full_join(x[[i]], y, by = c("geo_value", "time_value"))

  g[[i]] <- x[[i]] %>%
    filter(geo_value %in% tolower(state.abb)) %>%
    mutate(geo_num = as.integer(as.factor(geo_value))) %>%
    group_by(geo_value) %>%
    mutate(value = (value - Min(value)) / (Max(value) - Min(value)) +
             delta * (geo_num - 1)) %>%
    ungroup() %>%
    ggplot(aes(x = time_value, y = value, group = geo_value)) +
    labs(y = names[i]) + coord_cartesian(xlim = xlim, ylim = ylim) +
    geom_line(alpha = 0.5, color = colors[i], size = 0.3) +
    theme_void() +
    annotate("text", x = xp, y = yp, label = names[i],
             color = colors[i], angle = 90, size = 3) +
    theme(panel.background = element_rect(fill = "black"))
}

gg <- do.call(gridExtra::arrangeGrob, list(grobs = g, ncol = 1))
# PNAS wants 21 cm wide by 22.5 cm high
ggsave(file = "cover-graphic.pdf", gg, height = 22.5 / 2.54, width = 21 / 2.54)
```
